### 2016-03-09 paper/stereo.tex

\subsection{Swarm Fusion stereo}
We start with a relatively ``easy'' problem, a depthmap stereo problem
with unary and submodular pairwise terms. Parallel
alpha-expansion~\cite{delong} or hierarchical fusion~\cite{delong,olga}
with Graph-cuts (when submodular) or QPBO (when non-submodular) have
been the most effective techniques.
%
To make the comparison simple, we restrict our proposal generation to be
constant-label proposals, and limit to binary fusion so that Swarm
Fusion will also use either Graph-cuts or QPBO for the core
optimization. The main difference is that SF exchanges solutions among
threads throughout the process.
%
We use Middlebury stereo datasets for the experiments. Unary terms are
computed a standard Normalized Cross Correlation inside a $7\times 7$
window.

>>>>

\subsection{Swarm Fusion stereo}
We start with a relatively ``easy'' problem, a depthmap stereo problem
with unary and submodular pairwise terms. Parallel
alpha-expansion~\cite{delong} or hierarchical fusion~\cite{delong,olga}
with Graph-cuts (when submodular) or QPBO (when non-submodular) have
been the most effective techniques.
%
To make the comparison simple, we restrict our proposal generation to be
constant-label proposals, and limit to binary fusion so that Swarm
Fusion will also use either Graph-cuts or QPBO for the core
optimization. The main difference is that SF exchanges solutions among
threads throughout the process.

bottom middle example...

%
We use Middlebury stereo datasets for the experiments. Unary terms are
computed as the average Normalized Cross Correlation score between the
reference image and all the others inside a $7\times 7$ pixels
window. Pairwise terms are simple Pottz model. We multiply \yasu{X
value?} to the unary term to define the total energy.
